Arc Blanc: a real time ocean simulation framework

### 2025-01-10 paper.tex
We have corrected the index mistake v_z and not v_y
Remove excess term
Add "coupling" in abstract
Change the term used in scientific computing with cg to be more coherent with our article and JCGT

\begin{abstract}
	\small
	The oceans cover the vast majority of the Earth.
	Therefore, their simulation has many scientific, industrial and military interests, including computer graphics domain.
	By fully exploiting the multi-threading power of GPU and CPU, current state-of-the-art tools can achieve real-time ocean simulation, even if it is sometimes needed to reduce the physical realism for large scenes.
	Although most of the building blocks for implementing an ocean simulator are described in the literature, a clear explanation of how they interconnect is lacking.
	Hence, this paper proposes to bring all these components together, detailing all their interactions, in a comprehensive and fully described real-time framework that simulates the free ocean surface and the coupling between solids and fluid.
	This article also presents several improvements to enhance the physical realism of our model. 
	The two main ones are: 
	calculating the real-time velocity of ocean fluids at any depth; 
	computing the input of the fluid to solid algorithm.
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Context}
\label{subsec:intro-context}
Simulating the dynamics of an ocean and its surrounding elements remains an important objective in scientific computing.
As all the oceans encompass a substantial portion of the Earth's surface, understanding their behavior is of paramount importance in scientific, industrial, entertainment and military fields.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Free surface follows the velocity of water}
Next step assumes that the free surface follows the velocity of the water.
Hence, for all $\mathbf x$ on the horizontal axes at time $t + dt$ the height field is as follows:
\begin{equation}
	h(\mathbf{x^{\prime}}, t + dt) = h(\mathbf x, t) + {v_y}dt\label{equa:freeSurfaceFollowWater0}
\end{equation}
where:
\begin{equation}
	\mathbf{x^{\prime}} = \mathbf x + dt\left[\begin{array}{c}v_x\\ v_y\end{array}\right]
	\label{equa:freeSurfaceFollowWater1}
\end{equation}

@@

Neglecting the nonlinear terms in the Taylor expansion and reintegrating the development of $h(\mathbf{x^{\prime}}, t + dt)$ into Equation \ref{equa:freeSurfaceFollowWater0} and then dividing by $dt$ leads to the following result:
\begin{equation}
	\begin{aligned}
		\frac{h(\mathbf x, t + dt) - h(\mathbf x, t)}{dt} + v_x\frac{\partial h(\mathbf x, t)}{\partial x} + v_z\frac{\partial h(\mathbf x, t)}{\partial z} & = \frac{h(\mathbf x, t)}{dt} + v_y \\
		\frac{\partial h}{\partial t} + v_x\frac{\partial h}{\partial x} + v_z\frac{\partial h}{\partial z}                                                 & = v_y
	\end{aligned}
\end{equation}

>>>>

\begin{abstract}
	\small
	The oceans cover the vast majority of the Earth.
	Therefore, their simulation has many scientific, industrial and military interests, including computer graphics domain.
	By fully exploiting the multi-threading power of GPU and CPU, current state-of-the-art tools can achieve real-time ocean simulation, even if it is sometimes needed to reduce the physical realism for large scenes.
	Although most of the building blocks for implementing an ocean simulator are described in the literature, a clear explanation of how they interconnect is lacking.
	Hence, this paper proposes to bring all these components together, detailing all their interactions, in a comprehensive and fully described real-time framework that simulates the free ocean surface and the coupling between solids and fluid.
	This article also presents several improvements to enhance the physical realism of our model. 
	The two main ones are: 
	calculating the real-time velocity of ocean fluids at any depth; 
	computing the input of the fluid to solid coupling algorithm.
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Context}
\label{subsec:intro-context}
Simulating the dynamics of an ocean and its surrounding elements remains an important objective in computer graphics.
As all the oceans encompass a substantial portion of the Earth's surface, understanding their behavior is of paramount importance in scientific, industrial, entertainment and military fields.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Free surface follows the velocity of water}
Next step assumes that the free surface follows the velocity of the water.
Hence, for all $\mathbf x$ on the horizontal axes at time $t + dt$ the height field is as follows:
\begin{equation}
	h(\mathbf{x^{\prime}}, t + dt) = h(\mathbf x, t) + {v_y}dt\label{equa:freeSurfaceFollowWater0}
\end{equation}
where:
\begin{equation}
	\mathbf{x^{\prime}} = \mathbf x + dt\left[\begin{array}{c}v_x\\ v_z\end{array}\right]
	\label{equa:freeSurfaceFollowWater1}
\end{equation}

@@

Neglecting the nonlinear terms in the Taylor expansion and reintegrating the development of $h(\mathbf{x^{\prime}}, t + dt)$ into Equation \ref{equa:freeSurfaceFollowWater0} and then dividing by $dt$ leads to the following result:
\begin{equation}
	\begin{aligned}
		\frac{h(\mathbf x, t + dt) - h(\mathbf x, t)}{dt} + v_x\frac{\partial h(\mathbf x, t)}{\partial x} + v_z\frac{\partial h(\mathbf x, t)}{\partial z} & = v_y \\
		\frac{\partial h}{\partial t} + v_x\frac{\partial h}{\partial x} + v_z\frac{\partial h}{\partial z}                                                 & = v_y
	\end{aligned}
\end{equation}
